Universal Anonymous Signatures

### 2022-08-11 prism-backend/research/gsac/formal-uas.tex
Reviewed proofs of related schemes up to AC. Added ref to MPS eprint.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet((\upk,\usk),\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue defined by the issuer, and $\utrans$ being the transcript of
  the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
  signature,  both can in addition be used to modulate the behaviour of
  \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, the former is chosen on a
per-signature basis, probably after negotiation between signer and verifier, and
governs the information revealed at signing time. On the other hand, \finsp
governs the information that may be revealed after signing, and is defined by
openers when they set up their key pair. Thus even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function. In the sequel, we restrict to
\UAS-acceptable functions, defined as follows:

\begin{definition}{(\UAS-acceptable \fissue functions)}
  \label{def:uas-acc-func}
  We say that a \fissue function chosen from some family \famfissue is
  \UAS-acceptable if, conditioned on it returning a non-zero value, the
  value it produces is indistinguishable from random.
  % %
  % Similarly, a \feval function chosen from some family \famfeval is
  % \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
  % respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
\end{definition}

That is, at a high level we require that \fissue and \feval functions do not
reveal anything about the signer. \todo{Since the concept is quite intuitive, we
  defer the formal definition to \appref{app:XXX}}. We give in
\secref{ssec:generic-construction-uas}
a generic \CUASGen construction that assumes \UAS-acceptable functions. Next, we
define the concept of \CUASGen restrictions. Briefly, these are special cases of
our generic construction that target a concrete variant of the utility-privacy
tradeoff by defining concrete \fissue, \feval and \finsp functions. Security of
\CUASGen implies security of its restrictions, as long as the chosen functions
are \CUASGen-acceptable.

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\UGEN.] Adds a new user to the game, generating its keypair.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
  associated issuance function.
\item[\UCORR.] Corrupts an existing (and honest) user, by giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

        \procedure{$\UGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \KeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk) \\
          \HU \gets \HU \cup \lbrace \uid \rbrace \\
          \pcreturn \upk \\
        }

        \procedure{$\ISET(\uid,\fissue)$}{%
          \pcif \uid \notin \HU \cup \CU: \pcreturn \bot \\
          \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
          \ipk \gets \ISet(\UK[\uid],\fissue) \\
          \IK[\uid] \gets ((\ipk,\fissue),\PRVUK[\uid]) \\
          \pcif \uid \in \HU: \HI \gets \HI \cup \lbrace \uid \rbrace \\
          \pcif \uid \in \CU: \CI \gets \CI \cup \lbrace \uid \rbrace \\
          \pcreturn \ipk \\
        }

@@

@@

        % \procedure{$\CUGEN(\uid)$}{%          
        %   \pcif \uid \in \CU: \pcreturn \bot \\
        %   \CU \gets \CU \cup \lbrace \uid \rbrace \\          
        %   \pcif \uid \in \HU: \\
        %   \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
        %   \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
        %   \pcelse: \UK[\uid] = \bot \\          
        %   \pcreturn \top \\
        % }

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\cscid_0,\attrs)) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\cscid_1,\attrs)): \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\UGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

@@

The formal specification of the anonymity games is given in
\figref{fig:exp-uas-anonb}, where
$\OIssAnon \gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,
\OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
\gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,\OO,\UU\rbrace
\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.

@@

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure*}

@@

\begin{definition}{(Unforgeable issuance of \UAS)}
  \label{def:issue-forge-uas}  
  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
  \AdvForgeIssue is a negligible function of $1^\secpar$.
\end{definition}

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue defined by the issuer, and $\utrans$ being the transcript of
  the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk,\usk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
  \fissue functions must be \UAS-acceptable, as defined in
  \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
  signature,  both can in addition be used to modulate the behaviour of
  \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, the former is chosen on a
per-signature basis, probably after negotiation between signer and verifier, and
governs the information revealed at signing time. On the other hand, \finsp
governs the information that may be revealed after signing, and is defined by
openers when they set up their key pair. Thus even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function.

Concerning \fissue functions, our \UAS model requires them to be \UAS-acceptable
functions.  At a high level, this requires that \fissue functions do not reveal
anything about the signer's data used as input. This is formally captured in
\figref{fig:uas-acceptable}.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\usk,\lbrace (\cidi,\cattrs_i)
      \rbrace_{i\in[n]},\attrs) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

\begin{definition}{(\UAS-acceptable \fissue functions)}
  \label{def:uas-acc-func}
  A \fissue function is \UAS acceptable if, for any p.p.t. adversary \adv,
  $|\Pr[\Exp^{\UAS-acc-1}_\adv(1^\secpar)=1]-\Pr[\Exp^{\UAS-acc-0}_\adv
  (1^\secpar)=0]|$ is a negligible function of $1^\secpar$.
\end{definition}

A \UAS construction thus can only be secure if the \fissue function it uses is
\UAS-acceptable.
%
Next, we define the concept of \CUASGen restrictions. Briefly, these are special
cases of our generic construction that target a concrete variant of the
utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
functions. Security of \CUASGen implies security of its restrictions, as long as
the chosen functions are \CUASGen-acceptable.

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
\item[\HUGEN.] Adds a new corrupt user to the game, setting its \upk to the
  value given by the adversary.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
  associated issuance function.
\item[\UCORR.] Corrupts an existing (and honest) user, by giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \KeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk) \\
          \HU \gets \HU \cup \lbrace \uid \rbrace \\
          \pcreturn \upk \\
        }

@@

        \procedure{$\CUGEN(\uid,\upk)$}{%          
          \pcif \uid \in \HU \lor \CU: \pcreturn \bot \\
          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
          \UK[\uid] = (\upk,\bot) \\          
          \pcreturn \top \\
        }

        \procedure{$\ISET(\uid,\fissue)$}{%
          \pcif \uid \notin \HU \cup \CU: \pcreturn \bot \\
          \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
          \ipk \gets \ISet(\PUBUK[\uid],\PRVUK[\uid],\fissue) \\
          \IK[\uid] \gets ((\ipk,\fissue),\PRVUK[\uid]) \\
          \pcif \uid \in \HU: \HI \gets \HI \cup \lbrace \uid \rbrace \\
          \pcif \uid \in \CU: \CI \gets \CI \cup \lbrace \uid \rbrace \\
          \pcreturn \ipk \\
        }

@@

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\PRVUK[\cuid_0],\cscid_0,\attrs)) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\PRVUK[\cuid_1],\cscid_1,\attrs)):
          \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\PRVUK[\uid],\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\todo{All the following assumes \UAS-acceptable \fissue functions.}

@@

The formal specification of the anonymity games is given in
\figref{fig:exp-uas-anonb}.

@@

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.
    $\OIssAnon \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,
    \OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
    \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
    \CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$}
  \label{fig:exp-uas-anonb}
\end{figure*}

@@

% \begin{definition}{(Unforgeable issuance of \UAS)}
%   \label{def:issue-forge-uas}  
%   We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
%   $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
%   \AdvForgeIssue is a negligible function of $1^\secpar$.
% \end{definition}

% \begin{definition}{(Unforgeable signing of \UAS)}
%   \label{def:sign-forge-uas}  
%   We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
%   $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
%   \AdvForgeSign is a negligible function of $1^\secpar$.
% \end{definition}

% For short, we say that an \UAS scheme that has both unforgeable issuance and
% signing, is an unforgeable \UAS scheme.
